---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE
)
```

# workflowr-metrics

[![Travis-CI Build Status](https://travis-ci.org/workflowr/workflowr-metrics.svg?branch=master)](https://travis-ci.org/workflowr/workflowr-metrics)

Last update: `r Sys.time()`

```{r projects}
projects <- read.delim("data/github-projects.txt", stringsAsFactors = FALSE)
projects$count <- 1
projects$cumulative <- cumsum(projects$count)
```

* Number of workflowr projects on GitHub: `r projects$cumulative[nrow(projects)]`

```{r stars}
stars <- read.delim("data/github-stars.txt", stringsAsFactors = FALSE)
stars$count <- 1
stars$cumulative <- cumsum(stars$count)
```

* Stars of workflowr GitHub repository: `r stars$cumulative[nrow(stars)]`

```{r downloads}
downloads <- read.delim("data/cranlogs.txt", stringsAsFactors = FALSE)
downloads$cumulative <- cumsum(downloads$count)
```

* CRAN downloads: `r downloads$cumulative[nrow(downloads)]`

```{r watchers}
watchers <- read.delim("data/github-watchers.txt", stringsAsFactors = FALSE)
```

* Watchers of workflowr GitHub repository: `r nrow(watchers)`

```{r forks}
forks <- read.delim("data/github-forks.txt", stringsAsFactors = FALSE)
forks$count <- 1
forks$cumulative <- cumsum(forks$count)
```

* Forks of workflowr GitHub repository: `r forks$cumulative[nrow(forks)]`

```{r forks-updated}
# How many forks were updated more than 60 seconds after being created?
forks_updated <- sum(forks$update_difftime > 60)
```

* Forks of workflowr GitHub repository with updates: `r forks_updated`

```{r views}
views <- read.delim("data/github-views.txt", stringsAsFactors = FALSE)
views$cumulative <- cumsum(views$count)
```

* Views of workflowr GitHub repository: `r views$cumulative[nrow(views)]`

```{r clones}
clones <- read.delim("data/github-clones.txt", stringsAsFactors = FALSE)
clones$cumulative <- cumsum(clones$count)
```

* Clones of workflowr GitHub repository: `r clones$cumulative[nrow(clones)]`
