---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
library(lubridate)
knitr::opts_chunk$set(
  echo = FALSE
)
```

# workflowr-metrics

[![status](https://github.com/workflowr/workflowr-metrics/workflows/metrics/badge.svg)](https://github.com/workflowr/workflowr-metrics/actions/workflows/metrics.yaml)

Source: public GitHub repositories

Last update: `r Sys.time()`

```{r projects}
projects <- read.delim("data/github-projects.txt", stringsAsFactors = FALSE)
projects$count <- 1
projects$cumulative <- cumsum(projects$count)
```

```{r activity}
projects$last_push <- as_date(projects$last_push)
# weekly active projects
last_week <- today() - weeks(1)
stopifnot(is.Date(last_week))
weekly_active <- projects$last_push >= last_week
weekly_active_proj <- sum(weekly_active, na.rm = TRUE)
weekly_active_user <- length(unique(projects$user[weekly_active]))

# monthly active projects
last_month <- today() %m-% months(1)
stopifnot(is.Date(last_month))
monthly_active <- projects$last_push >= last_month
monthly_active_proj <- sum(monthly_active, na.rm = TRUE)
monthly_active_user <- length(unique(projects$user[monthly_active]))
```

* Weekly active projects (unique users): `r weekly_active_proj` (`r weekly_active_user`)

* Monthly active projects (unique users): `r monthly_active_proj` (`r monthly_active_user`)

* Number of workflowr projects on GitHub: `r projects$cumulative[nrow(projects)]`

```{r activity-save}
activity_line <- sprintf("%s\t%d\t%d\t%d\t%d\n", today(),
                         weekly_active_proj, weekly_active_user,
                         monthly_active_proj, monthly_active_user)
cat(activity_line, file = "data/activity.txt", append = TRUE)
```

```{r stars}
stars <- read.delim("data/github-stars.txt", stringsAsFactors = FALSE)
stars$count <- 1
stars$cumulative <- cumsum(stars$count)
```

* Stars of workflowr GitHub repository: `r stars$cumulative[nrow(stars)]`

```{r downloads}
downloads <- read.delim("data/cranlogs.txt", stringsAsFactors = FALSE)
downloads$cumulative <- cumsum(downloads$count)
```

* CRAN downloads: `r downloads$cumulative[nrow(downloads)]`

```{r packagerank}
packagerank <- read.delim("data/packagerank.txt", stringsAsFactors = FALSE)
packagerank_latest <- packagerank[nrow(packagerank), ]
```

* CRAN package percentile (on `r packagerank_latest$date`): `r packagerank_latest$percentile`

```{r watchers}
watchers <- read.delim("data/github-watchers.txt", stringsAsFactors = FALSE)
```

* Watchers of workflowr GitHub repository: `r nrow(watchers)`

```{r forks}
forks <- read.delim("data/github-forks.txt", stringsAsFactors = FALSE)
forks$count <- 1
forks$cumulative <- cumsum(forks$count)
```

* Forks of workflowr GitHub repository: `r forks$cumulative[nrow(forks)]`

```{r forks-updated}
# How many forks were updated more than 60 seconds after being created?
forks_updated <- sum(forks$update_difftime > 60, na.rm = TRUE)
```

* Forks of workflowr GitHub repository with updates: `r forks_updated`

```{r views}
views <- read.delim("data/github-views.txt", stringsAsFactors = FALSE)
views$cumulative <- cumsum(views$count)
```

* Views of workflowr GitHub repository: `r views$cumulative[nrow(views)]`

```{r clones}
clones <- read.delim("data/github-clones.txt", stringsAsFactors = FALSE)
clones$cumulative <- cumsum(clones$count)
```

* Clones of workflowr GitHub repository: `r clones$cumulative[nrow(clones)]`
